Measurement and Probability in Fuzzy Quantum Theories

### 2017-03-05 prop_iop.tex
prop_iop.tex \section{Cryptodeterminism} Fix notation...

\begin{definition}[Classical Cryptodeterministic Measure]\label{def:CryptodeterministicMeasures}Given
the set of events~$\events$, a \emph{classical cryptodeterministic
measure} is a function~$\pmeas:\events\rightarrow\left\{ 0,1\right\} $
such that: 
\begin{itemize}
\item $\pmeas(\emptyset)=0$, 
\item $\pmeas(\Omega)=1$, 
\item for every event $E$, $\pmeas\left(\Omega\backslash E\right)=1-\pmeas\left(E\right)$
where $\Omega\backslash E$ is the complement event of $E$, and 
\item for every collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise
disjoint events, $\pmeas\left(\bigcup_{i=1}^{N}E_{i}\right)=\sum_{i=1}^{N}\pmeas(E_{i})$. 
\end{itemize}
\end{definition}

\begin{example}[Two-coin experiment with cryptodeterministic measure]\label{ex4}Except
the prefect prediction, a cryptodeterministic measure can model the
belief of events which has already happened. For example, if we tossed
the coin in example~\ref{ex1}, and saw $HH$, our belief of which
event has happened is represented by the following example.
\begin{equation}
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\bar{\mu}(\emptyset) & = & 0\\
\bar{\mu}(\{HH\}) & = & 1\\
\bar{\mu}(\{HT\}) & = & 0\\
\bar{\mu}(\{TH\}) & = & 0\\
\bar{\mu}(\{TT\}) & = & 0\\
\bar{\mu}(\{HH,HT\}) & = & 1\\
\bar{\mu}(\{HH,TH\}) & = & 1\\
\bar{\mu}(\{HH,TT\}) & = & 1
\end{array} & \begin{array}{rcl}
\bar{\mu}(\{HT,TH\}) & = & 0\\
\bar{\mu}(\{HT,TT\}) & = & 0\\
\bar{\mu}(\{TH,TT\}) & = & 0\\
\bar{\mu}(\{HH,HT,TH\}) & = & 1\\
\bar{\mu}(\{HH,HT,TT\}) & = & 1\\
\bar{\mu}(\{HH,TH,TT\}) & = & 1\\
\bar{\mu}(\{HT,TH,TT\}) & = & 0\\
\bar{\mu}(\{HH,HT,TH,TT\}) & = & 1
\end{array}\end{array}
\end{equation}
\end{example}

\noindent The ability to predict classical events unambiguously rather
than probabilistically inspired Einstein, Podolsky, and Rosen to ask
whether quantum mechanics has any chance to be improved and predict
in the same way~\cite{EPR1935,peres1995quantum,544199,Mermin2007}.
This question can be formulated by whether quantum mechanics could
be modeled by quantum cryptodeterministic measures.

\begin{definition}[Quantum Cryptodeterministic Measure]\label{def:QuantumCryptodeterministicMeasures}Given
a Hilbert space $\Hilb$ with its set of events~$\events$, a \emph{quantum
cryptodeterministic measure} is a function~$\pmeas:\events\rightarrow\left\{ 0,1\right\} $
such that: 
\begin{itemize}
\item $\pmeas(\mathbb{0})=0$, 
\item $\pmeas(\mathbb{1})=1$, 
\item for every event $P$, $\pmeas\left(\Omega\backslash P\right)=1-\pmeas\left(P\right)$
where $\Omega\backslash P$ is the complement event of $P$, and 
\item for every collection $\left\{ P_{i}\right\} _{i=1}^{N}$ of pairwise
disjoint events, $\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\pmeas(P_{i})$. 
\end{itemize}
\end{definition}

@@

\begin{thm}[Kochen-Specker~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}]\label{thm:Kochen-Specker}Given
a Hilbert space of dimension~$d\ge3$, there is no cryptodeterministic
measure~$\pmeas:\events\rightarrow\left\{ 0,1\right\} $.\end{thm}

\noindent Although sharing a lot of similarity, the Kochen-Specker
theorem highlight the difference between quantum and classical measures.
When we think a cryptodeterministic measure as a model of pasted events,
the Kochen-Specker theorem also consistent with the usual interpretation
of the quantum theory: we should not ask whether an event happened
or not if an event is incompatible with the event really happened;
events compatible with the event really happened are the only askable
events.

@@

\begin{tabular}{ccc|cccc} 
\br 
\multicolumn{3}{c}{Commuting observables} & \multicolumn{4}{c}{Common eigenbasis} \\
\mr 
$\mathbb{1}\otimes\sigma_{z}$ & $\sigma_{z}\otimes\mathbb{1}$ & $\sigma_{z}\otimes\sigma_{z}$ & $(1, 0, 0, 0)$ & $(0, 1, 0, 0)$ & $(0, 0, 1, 0)$ & $(0, 0, 0, 1)$ \\
$\sigma_{x}\otimes\mathbb{1}$ & $\mathbb{1}\otimes\sigma_{x}$ & $\sigma_{x}\otimes\sigma_{x}$ & $(1, 1, 1, 1)$ & $(1, -1, 1, -1)$ & $(1, 1, -1, -1)$ & $(1, -1, -1, 1)$ \\
$\sigma_{x}\otimes\sigma_{z}$ & $\sigma_{z}\otimes\sigma_{x}$ & $\sigma_{y}\otimes\sigma_{y}$ & $(1, 1, 1, -1)$ & $(1, 1, -1, 1)$ & $(1, -1, 1, 1)$ & $(-1, 1, 1, 1)$ \\
$\mathbb{1}\otimes\sigma_{z}$ & $\sigma_{x}\otimes\mathbb{1}$ & $\sigma_{x}\otimes\sigma_{z}$ & $(1, 0, 1, 0)$ & $(0, 1, 0, 1)$ & $(1, 0, -1, 0)$ & $(0, 1, 0, -1)$ \\
$\sigma_{z}\otimes\mathbb{1}$ & $\mathbb{1}\otimes\sigma_{x}$ & $\sigma_{z}\otimes\sigma_{x}$ & $(1, 1, 0, 0)$ & $(1, -1, 0, 0)$ & $(0, 0, 1, 1)$ & $(0, 0, 1, -1)$ \\
$\sigma_{z}\otimes\sigma_{z}$ & $\sigma_{x}\otimes\sigma_{x}$ & $\sigma_{y}\otimes\sigma_{y}$ & $(0, 1, 1, 0)$ & $(0, 1, -1, 0)$ & $(1, 0, 0, 1)$ & $(1, 0, 0, -1)$ \\
\br 
\end{tabular} 
\end{table}
Since observables in equation~(\ref{eq:MerminSquare}) are not projections,
if we want to reformulate the above argument in the language of quantum
probability measures, we first need to find the common eigenbasis
of each row and column, and consider the projections to each eigenvectors.
Let $\mathcal{T}_{24}$ denote all eigenstates listed in table~\ref{table:commonBasis}.
The Kochen-Specker theorem could then be proved by showing there is
no function~$v:\events'\rightarrow\left\{ 0,1\right\} $ satisfying
equation~(\ref{eq:Kochen-Specker-Rules}), where 
\begin{equation}
\events'=\set{\sum_{i=1}^{N}\proj{\psi_{i}}}{\textrm{mutually orthogonal }\left\{ \ket{\psi_{i}}\right\} _{i=1}^{N}\subseteq\mathcal{T}_{24}}
\end{equation}
which is a sub-event space defined in definition~\ref{def:sub-event-space}.
This kind of $v$ is actually a quantum cryptodeterministic measure.
Since a cryptodeterministic measure are a special case of real-valued
probability measure, by theorem~\ref{lemma:classical-probability-measures},
the quantum cryptodeterministic measure~$v$ exists if and only if
there exists a frame function~$f:\mathcal{T}_{24}\rightarrow\left\{ 0,1\right\} $
which should at least satisfy
\begin{equation}\eqalign{ 
1 = f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 0) + f(0, 0, 0, 1)\textrm{ and}\\
1 = f(-1, 1, 1, 1) + f(1, -1, 1, 1) + f(1, 1, -1, 1) + f(1, 1, 1, -1)
}\label{eq:Kernaghan-1}\end{equation}
because of table~\ref{table:commonBasis}. $f$ should also satisfy
the following equations since the vectors in each equation form an
orthogonal basis~\cite{Kernaghan1994,peres1995quantum}.
\begin{equation}\eqalign{ 
1 = f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 1) + f(0, 0, 1, -1)\textrm{ ,}\\
1 = f(1, 0, 0, 0) + f(0, 0, 1, 0) + f(0, 1, 0, 1) + f(0, 1, 0, -1)\textrm{ ,}\\
1 = f(1, 0, 0, 0) + f(0, 0, 0, 1) + f(0, 1, 1, 0) + f(0, 1, -1, 0)\textrm{ ,}\\
1 = f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(1, 0, 1, 0) + f(0, 1, 0, -1)\textrm{ ,}\\
1 = f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(0, 1, 1, 0) + f(1, 0, 0, -1)\textrm{ ,}\\
1 = f(1, 1, -1, 1) + f(1, 1, 1, -1) + f(0, 0, 1, 1) + f(1, -1, 0, 0)\textrm{ ,}\\
1 = f(0, 1, -1, 0) + f(1, 0, 0, -1) + f(1, 1, 1, 1) + f(1, -1, -1, 1)\textrm{ ,}\\
1 = f(0, 0, 1, -1) + f(1, -1, 0, 0) + f(1, 1, 1, 1) + f(1, 1, -1, -1)\textrm{ ,}\\
1 = f(1, 0, 1, 0) + f(0, 1, 0, 1) + f(1, 1, -1, -1) + f(1, -1, -1, 1)
}\label{eq:Kernaghan-2}\end{equation}
In equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2}, there
are odd number of equations, but each $f\left(\alpha_{0},\alpha_{1},\alpha_{2},\alpha_{3}\right)$
occurs twice. Therefore, there is no frame function~$f:\mathcal{T}_{24}\rightarrow\left\{ 0,1\right\} $
satisfying equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2}.

>>>>

\begin{definition}[Classical Cryptodeterministic Measure]\label{def:CryptodeterministicMeasures}Given
the set of events~$\events$, a \emph{classical cryptodeterministic
measure} is a function~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\} $
such that: 
\begin{itemize}
\item $\mu^{\mathrm{D}}(\emptyset)=0$, 
\item $\mu^{\mathrm{D}}(\Omega)=1$, 
\item for every event $E$, $\mu^{\mathrm{D}}\left(\Omega\backslash E\right)=1-\mu^{\mathrm{D}}\left(E\right)$
where $\Omega\backslash E$ is the complement event of $E$, and 
\item for every collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise
disjoint events, $\mu^{\mathrm{D}}\left(\bigcup_{i=1}^{N}E_{i}\right)=\sum_{i=1}^{N}\mu^{\mathrm{D}}(E_{i})$. 
\end{itemize}
\end{definition}

\begin{example}[Two-coin experiment with cryptodeterministic measure]\label{ex4}Except
the prefect prediction, a cryptodeterministic measure can model the
belief of events which has already happened. For example, if we tossed
the coin in example~\ref{ex1}, and saw $HH$, our belief of which
event has happened is represented by the following example.
\begin{equation}
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\mu^{\mathrm{D}}(\emptyset) & = & 0\\
\mu^{\mathrm{D}}(\{HH\}) & = & 1\\
\mu^{\mathrm{D}}(\{HT\}) & = & 0\\
\mu^{\mathrm{D}}(\{TH\}) & = & 0\\
\mu^{\mathrm{D}}(\{TT\}) & = & 0\\
\mu^{\mathrm{D}}(\{HH,HT\}) & = & 1\\
\mu^{\mathrm{D}}(\{HH,TH\}) & = & 1\\
\mu^{\mathrm{D}}(\{HH,TT\}) & = & 1
\end{array} & \begin{array}{rcl}
\mu^{\mathrm{D}}(\{HT,TH\}) & = & 0\\
\mu^{\mathrm{D}}(\{HT,TT\}) & = & 0\\
\mu^{\mathrm{D}}(\{TH,TT\}) & = & 0\\
\mu^{\mathrm{D}}(\{HH,HT,TH\}) & = & 1\\
\mu^{\mathrm{D}}(\{HH,HT,TT\}) & = & 1\\
\mu^{\mathrm{D}}(\{HH,TH,TT\}) & = & 1\\
\mu^{\mathrm{D}}(\{HT,TH,TT\}) & = & 0\\
\mu^{\mathrm{D}}(\{HH,HT,TH,TT\}) & = & 1
\end{array}\end{array}
\end{equation}
\end{example}

The ability to predict classical events unambiguously rather than
probabilistically inspired Einstein, Podolsky, and Rosen to ask whether
quantum mechanics has any chance to be improved and predict in the
same way~\cite{EPR1935,peres1995quantum,544199,Mermin2007}. This
question can be formulated by whether quantum mechanics could be modeled
by quantum cryptodeterministic measures.

\begin{definition}[Quantum Cryptodeterministic Measure]\label{def:QuantumCryptodeterministicMeasures}Given
a Hilbert space $\Hilb$ with its set of events~$\events$, a \emph{quantum
cryptodeterministic measure} is a function~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\} $
such that: 
\begin{itemize}
\item $\mu^{\mathrm{D}}(\mathbb{0})=0$, 
\item $\mu^{\mathrm{D}}(\mathbb{1})=1$, 
\item for every event $P$, $\mu^{\mathrm{D}}\left(\Omega\backslash P\right)=1-\mu^{\mathrm{D}}\left(P\right)$
where $\Omega\backslash P$ is the complement event of $P$, and 
\item for every collection $\left\{ P_{i}\right\} _{i=1}^{N}$ of pairwise
disjoint events, $\mu^{\mathrm{D}}\left(\bigcup_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\mu^{\mathrm{D}}(P_{i})$. 
\end{itemize}
\end{definition}

@@

\begin{thm}[Kochen-Specker~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}]\label{thm:Kochen-Specker}Given
a Hilbert space of dimension~$d\ge3$, there is no cryptodeterministic
measure~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\} $.\end{thm}

Although sharing a lot of similarity, the Kochen-Specker theorem highlight
the difference between quantum and classical measures. When we think
a cryptodeterministic measure as a model of pasted events, the Kochen-Specker
theorem also consistent with the usual interpretation of the quantum
theory: we should not ask whether an event happened or not if an event
is incompatible with the event really happened; events compatible
with the event really happened are the only askable events.

@@

\begin{tabular}{ccc|cccc} 
\br 
\multicolumn{3}{c}{Commuting observables} & \multicolumn{4}{c}{Common eigenbasis} \\
\mr 
$\mathbb{1}\otimes\sigma_{z}$ & $\sigma_{z}\otimes\mathbb{1}$ & $\sigma_{z}\otimes\sigma_{z}$ & $(1, 0, 0, 0)$ & $(0, 1, 0, 0)$ & $(0, 0, 1, 0)$ & $(0, 0, 0, 1)$ \\
$\sigma_{x}\otimes\mathbb{1}$ & $\mathbb{1}\otimes\sigma_{x}$ & $\sigma_{x}\otimes\sigma_{x}$ & $(1, 1, 1, 1)$ & $(1, -1, 1, -1)$ & $(1, 1, -1, -1)$ & $(1, -1, -1, 1)$ \\
$\sigma_{x}\otimes\sigma_{z}$ & $\sigma_{z}\otimes\sigma_{x}$ & $\sigma_{y}\otimes\sigma_{y}$ & $(1, 1, 1, -1)$ & $(1, 1, -1, 1)$ & $(1, -1, 1, 1)$ & $(-1, 1, 1, 1)$ \\
$\mathbb{1}\otimes\sigma_{z}$ & $\sigma_{x}\otimes\mathbb{1}$ & $\sigma_{x}\otimes\sigma_{z}$ & $(1, 0, 1, 0)$ & $(0, 1, 0, 1)$ & $(1, 0, -1, 0)$ & $(0, 1, 0, -1)$ \\
$\sigma_{z}\otimes\mathbb{1}$ & $\mathbb{1}\otimes\sigma_{x}$ & $\sigma_{z}\otimes\sigma_{x}$ & $(1, 1, 0, 0)$ & $(1, -1, 0, 0)$ & $(0, 0, 1, 1)$ & $(0, 0, 1, -1)$ \\
$\sigma_{z}\otimes\sigma_{z}$ & $\sigma_{x}\otimes\sigma_{x}$ & $\sigma_{y}\otimes\sigma_{y}$ & $(0, 1, 1, 0)$ & $(0, 1, -1, 0)$ & $(1, 0, 0, 1)$ & $(1, 0, 0, -1)$ \\
\br 
\end{tabular} 
\end{table}
Since observables in equation~(\ref{eq:MerminSquare}) are not projections,
if we want to reformulate the above argument in the language of quantum
probability measures, we first need to find the common eigenbasis
of each row and column, and consider the projections to each eigenvectors.
Let $\mathcal{T}_{24}$ denote all eigenstates listed in table~\ref{table:commonBasis}.
The Kochen-Specker theorem could then be proved by showing there is
no function~$v:\events'\rightarrow\left\{ 0,1\right\} $ satisfying
equation~(\ref{eq:Kochen-Specker-Rules}), where 
\begin{equation}
\events'=\set{\sum_{i=1}^{N}\proj{\psi_{i}}}{\textrm{mutually orthogonal }\left\{ \ket{\psi_{i}}\right\} _{i=1}^{N}\subseteq\mathcal{T}_{24}}
\end{equation}
which is a sub-event space defined in definition~\ref{def:sub-event-space}.
This kind of $v$ is actually a quantum cryptodeterministic measure.
Since a cryptodeterministic measure are a special case of real-valued
probability measure, by theorem~\ref{lemma:classical-probability-measures},
the quantum cryptodeterministic measure~$v$ exists if and only if
there exists a frame function~$f:\mathcal{T}_{24}\rightarrow\left\{ 0,1\right\} $
which should at least satisfy
\begin{equation}\eqalign{ 
1 = f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 0) + f(0, 0, 0, 1)\textrm{ and}\\
1 = f(-1, 1, 1, 1) + f(1, -1, 1, 1) + f(1, 1, -1, 1) + f(1, 1, 1, -1)
}\label{eq:Kernaghan-1}\end{equation}
because of table~\ref{table:commonBasis}. $f$ should also satisfy
the following equations since the vectors in each equation form an
orthogonal basis~\cite{Kernaghan1994,peres1995quantum}:
\begin{equation}\eqalign{ 
1 = f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 1) + f(0, 0, 1, -1)\textrm{ ,}\\
1 = f(1, 0, 0, 0) + f(0, 0, 1, 0) + f(0, 1, 0, 1) + f(0, 1, 0, -1)\textrm{ ,}\\
1 = f(1, 0, 0, 0) + f(0, 0, 0, 1) + f(0, 1, 1, 0) + f(0, 1, -1, 0)\textrm{ ,}\\
1 = f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(1, 0, 1, 0) + f(0, 1, 0, -1)\textrm{ ,}\\
1 = f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(0, 1, 1, 0) + f(1, 0, 0, -1)\textrm{ ,}\\
1 = f(1, 1, -1, 1) + f(1, 1, 1, -1) + f(0, 0, 1, 1) + f(1, -1, 0, 0)\textrm{ ,}\\
1 = f(0, 1, -1, 0) + f(1, 0, 0, -1) + f(1, 1, 1, 1) + f(1, -1, -1, 1)\textrm{ ,}\\
1 = f(0, 0, 1, -1) + f(1, -1, 0, 0) + f(1, 1, 1, 1) + f(1, 1, -1, -1)\textrm{ ,}\\
1 = f(1, 0, 1, 0) + f(0, 1, 0, 1) + f(1, 1, -1, -1) + f(1, -1, -1, 1)\textrm{ .}
}\label{eq:Kernaghan-2}\end{equation}
In equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2}, there
are odd number of equations, but each $f\left(\alpha_{0},\alpha_{1},\alpha_{2},\alpha_{3}\right)$
occurs twice. Therefore, there is no frame function~$f:\mathcal{T}_{24}\rightarrow\left\{ 0,1\right\} $
satisfying equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2}.
